### 2023-09-10 proofs/tex/ord-lemmas.tex
Collision-free bijection

Next, we define the notion of a collision free bijection.
It allows us to deal with the situations when
the domain and the range of the bijection overlap.
Intuitively,

@@

>>>>

Next we make a set-theoretical observation
that will be useful further.
In general, any injective function (its image)
distributes over set intersection.
However, for convenience we allow the bijections
on variables to be applied
\emph{outside of their domains}
(as identities), which may violate
the injectivity. To deal with these cases, 
we define a special notion of
bijections collision-free on certain sets
in such a way that
a bijection that is collision-free on $P$ and $Q$,
distributes over intersection of $P$ and $Q$.

@@

\begin{observation}
  Suppose that $\mu : A \leftrightarrow B$ is a bijection between two sets of variables,
  and $\mu$ is collision free on $P$ and $Q$.
  Then $\mu(P \cap Q) = \mu(P) \cap \mu(Q)$.
\end{observation}
